\documentclass[a4paper,11pt]{memoir}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}    
\usepackage[margin=2.5cm]{geometry}
\usepackage{listings,hyperref,color}

\usepackage{titlesec}

\usepackage{tipa}

\definecolor{lightgray}{rgb}{0.95,0.95,0.95}
\definecolor{lightgreen}{rgb}{0,0.6,0}

\titleformat{\section}
{\normalfont\large\bfseries}
{\thesection\hskip 9pt\textpipe\hskip 9pt}
{0pt}
{}

\titleformat{\chapter}
{\normalfont\Large\bfseries}
{\thechapter\hskip 9pt\textpipe\hskip 9pt}
{0pt}
{}

\lstset{
	frame=tblr,
	keywordstyle=\color{blue}\textbf,
	backgroundcolor=\color{lightgray},
	commentstyle=\color{lightgreen},
	basicstyle=\footnotesize,
	tabsize=2
}

\begin{document}
\pagestyle{plain}
\chapter{Self Study 5}

\section{How many Danish language movies are in the database?}
\lstinputlisting[language=sql]{sql/1.sql}
\lstinputlisting{sql_res/1.sql}

\section{For each year, what is the total number of reviews to movies from that year?}
\lstinputlisting[language=sql]{sql/2.sql}
\lstinputlisting{sql_res/2.sql}

\section{Which movies have John Travolta and Uma Thurman starred in together?}
\lstinputlisting[language=sql]{sql/3.sql}
\lstinputlisting{sql_res/3.sql}

\section{How many actors and directors have a first name starting with ``Q''?}
\lstinputlisting[language=sql]{sql/4.sql}
\lstinputlisting{sql_res/4.sql}

\section{How many users rated at least 3 movies?}
\lstinputlisting[language=sql]{sql/5.sql}
\lstinputlisting{sql_res/5.sql}

\section{What is the name and birth year of all actors in ``Pulp Fiction''?}
\lstinputlisting[language=sql]{sql/6.sql}
\lstinputlisting{sql_res/6.sql}

\section{What are the titles and years of all movies from the 1980s that John Travolta starred in?}
\lstinputlisting[language=sql]{sql/7.sql}
\lstinputlisting{sql_res/7.sql}

\section{What are the top-2 highest rated movies (average) from the 1990s according to the users?}
\lstinputlisting[language=sql]{sql/8.sql}
\lstinputlisting{sql_res/8.sql}

\section{What are the top-2 highest rated movies (average) from the 1990s according to at least 2 users?}
\lstinputlisting[language=sql]{sql/9.sql}
\lstinputlisting{sql_res/9.sql}

\section{In 1994, what was the average rating of a movie for each language?}
\lstinputlisting[language=sql]{sql/10.sql}
\lstinputlisting{sql_res/10.sql}

\section{Which actors in ``Pulp Fiction'' have never, before or after, starred in the same movie as one of the other actors in ``Pulp Fiction''?}
\lstinputlisting[language=sql]{sql/11.sql}
\lstinputlisting{sql_res/11.sql}

\section{Which movie starring John Travolta has the highest user ratings?}
\lstinputlisting[language=sql]{sql/12.sql}
\lstinputlisting{sql_res/12.sql}

\section{How many actresses have not been alive at the same time as Charles Chaplin?}
\lstinputlisting[language=sql]{sql/13.sql}
\lstinputlisting{sql_res/13.sql}

\section{What is the average rating of movies from each genre?}
\lstinputlisting[language=sql]{sql/14.sql}
\lstinputlisting{sql_res/14.sql}

\section{What is the average rating of movies from each genre? List only genres with at least 2 ratings.}
\lstinputlisting[language=sql]{sql/15.sql}
\lstinputlisting{sql_res/15.sql}

\section{Which movie has the largest number of 2-link references?}
\lstinputlisting[language=sql]{sql/16_2.sql}
\lstinputlisting{sql_res/16.sql}

\section{How many actors have also been active as director of at least one movie?}
\lstinputlisting[language=sql]{sql/17_2.sql}
\lstinputlisting{sql_res/17.sql}


\section{Which two genres are most often linked to the same movie? (Note that each movie has a set of genres.)}
\lstinputlisting[language=sql]{sql/18.sql}
\lstinputlisting{sql_res/18.sql}

\end{document}